Fast Fourier transformation of electromagnetic data for computationally expensive kernels

### 2021-02-26 ManuscriptTime.tex
EOW

@@

>>>>

\added{Note to reviewers: This entire section is new, without being all
marked in green.}

@@

The Cole-Cole model \citep[CCM, ][]{JCP.41.Cole}, written in terms of
conductivities instead of electric permittivities as by the original authors,
is given by
%
\begin{equation}
  \sigma(\omega) = \sigma_\infty + \frac{\sigma_0 - \sigma_\infty}{1 +
    (\rm{i}\omega\tau)^c}\ ,
  \label{eq:ccm}
\end{equation}
%
where $\sigma_0$ and $\sigma_\infty$ refer to the low-frequency and
high-frequency conductivity values, respectively, $\tau$ is the central
relaxation time, and $c$ the CCM exponent describing the broadness of the
relaxation time distribution. Note that this model slightly differs from the
one phrased in terms of resistivities given by \cite{GEO.78.Pelton}, see, e.g.,
\cite{GJI.13.Tarasov}.
%
\begin{figure}
  \centering
  \includegraphics[width=\fwidth]{11-cole-cole-model}
  \caption{}
  \label{fig:CCM}
\end{figure}
%

It required only 30 frequencies from 1.5e-8 to 8.3\,Hz, instead of the 244
frequencies from 1.5e-8 to 6.8e6\,Hz required by the digital filter (201\,pt
filter from Key, 2012). Besides the fact that the responses for the higher
frequencies can be set to zero it is also sufficient to only compute every
5th of the required frequencies.

low frequencies cannot be 'interpolated'; however, other tricks could be
implemented. The DC values (so low frequencies or late times) is the same
independent of the IP effect. This makes it possible to estimate the DC value
with the IP-free model which does not require very low frequencies, and use
consequently this DC value to interpolate the low frequencies.
